Predicting Solid State Qubit Candidates

### 2021-08-10 paper.tex
Updates from Overleaf

\section{Introduction}

\section{Theoretical Background and Experimental Data}

\section{Results and Discussions}

>>>>

%Where to submit? 
% npj Quantum Information  or npj Computational Materials are options I am familiar with 
%

\section{Introduction}
To sustain the digital world’s increasing computational demand, alternatives to the classical computer must be explored. The quantum computer, together with the complementary quantum technologies of sensing and communication, is becoming a frontrunner in the race for solutions. 
Discuss recent benchmarks for quantum computing \cite{Arute_2019}.

Limitations of quantum computing and technology building blocks. Drawbacks of superconductors. Semiconductors are a promising platform. Example of NV center in diamond \cite{Doherty_2013}.

%From thesis - rewrite 
Unfortunately, there are substantial challenges associated with the modern quantum platforms simultaneously as the selection of quantum platforms are slim. The majority of discoveries of potential quantum platforms have so far happened by serendipity, and there is an urgent need for new and better materials that can escalate the effort for a sustainable future.

The fourth science paradigm introduces the potential of targeted search for promising material systems to act as qubit hosts. 
Herein, we provide a framework for the automatic discovery of promising solid-state material hosts using machine learning methods. 
Initial database building similar to Ferrenti et al [].

\section{Theoretical Background and Experimental Data} 
%subsections are potential topics, not necessarily subsections we will actually include

\subsection{Quantum host material requirements}
%What parameters are we looking for?

\subsection{The semiconductor platform}
%Experimental findings

\subsection{Introduction to DFT} 
%Data formats

\subsection{Databases} 
%Materials project, AFLOW, Open Quantum, JARVIS

\section{Methodology}
\subsection{Materials informatics} 
Mining

Screening

\subsection{Machine learning}

\section{Results and Discussion}
\subsection{}
